Galois Slicing as Differentiation

### 2025-07-11 main/approx-as-tangents.tex
[ tex ] more line saving

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  An example that is conditionally multiplicative, but does not admit
  a backwards map of approximations (from \citet[just
  before Lemma 12.2.3]{amadio-curien}, originally due to Berry) is given by defining
  $\mathrm{unstable} : D \to \{\bot \sqsubseteq \top\}$, where
  $D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots
  \sqsubseteq 1 \sqsubseteq 0$, as $\mathrm{unstable}(\bot) = \bot$
  and $\mathrm{unstable}(n) = \top$. This is monotone, and preserves
  meets in every $\downset{x}$. However, there is no ``best'' (i.e.,
  least) input that gives us any finite output.
\end{example}

>>>>

\begin{example}[Is Conditional Multiplicativity Enough?]
  \label{ex:non-stable-function}
  An example that is conditionally multiplicative, but does not admit
  a backwards map of approximations (from \citet[just before Lemma
  12.2.3]{amadio-curien}, originally due to Berry) is given by
  $\mathrm{unstable} : D \to \{\bot \sqsubseteq \top\}$, where
  $D = \bot \sqsubseteq \cdots \sqsubseteq n \sqsubseteq \cdots
  \sqsubseteq 1 \sqsubseteq 0$, as $\mathrm{unstable}(\bot) = \bot$
  and $\mathrm{unstable}(n) = \top$. This is monotone, and preserves
  meets in every $\downset{x}$. But there is no ``best'' (i.e., least)
  input that gives us any finite output.
\end{example}
